AI Safety for High Energy Physics

### 2019-10-03 documentation/manuscript.tex
forgot to add figure for HL network

\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{figures/adv_classifer_response.pdf}
\caption{
Comparison of the adversary's effect on signal and background distributions.
}
\end{figure}

>>>>

\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{figures/adv_classifer_response.pdf}
\caption{
Comparison of the adversary's effect on signal and background distributions for the low-level network.
}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{figures/adv_classifer_response_HL.pdf}
\caption{
Comparison of the adversary's effect on signal and background distributions for the high-level network.
}
\end{figure}
